### 2014-03-30 LaTeX/RhodiumLit.tex
double space, added lit
Updated bib.

That civil wars negatively impact economic performance, while in line with the ``war ruin'' hypothesis, runs counter to the ``war renewal'' hypothesis.  Some scholars have argued that wars, international wars in particular, can spur economic development\footnote{For a review of this discussion, see \cite{rasler:thompson:1985}}.  The prevailing wisdom with regard to civil war, however, is that outcomes of this nature are the exception rather than the rule.  In a test of economic and social determinants of post-conflict recovery in the context of civil war, \cite{kang:meernick:2005} find that these conflicts can lead, under different conditions, to either rapid or stagnant economic recovery.  They conclude that the long-term economic impacts of civil war are largely dependent on post-war governance and foreign assistance.  They also find, perhaps unsuprisingly, that aggregate estimates of conflict destructiveness are negatively correlated with long-term growth.

Not only do several studies link civil war to domestic economic performance, there is also evidence that civil wars have regional economic consequences.  \cite{murdoch:sandler:2002} find some evidence that states neighboring civil war states are more likely to experience poor short-term economic performance.  They attribute this effect to the disruption of trade and uncertainty about the potential for conflict to spread across the border.  In a follow up study, \cite{murdoch:sandler:2002} suggest that the spatial dispersion of economic effects from civil conflict differ from region to region.

@@

\cite{berman:couttenier:2013} explore another sub-state determinant of civil conflict.  Recognizing that economic shocks are associated with changes to the probability of civil conflict,\footnote{For more, see \cite{miguel:etal:2004} and \cite{dube:vargas:forthcoming}.} they seek to determine where conflict will emerge when these shocks occur.  Given an external economic shock in a trading partner, Berman and Couttenier expect that states should be at an increased risk of experiencing conflict.  However, not all locations within a state will feel the effects equally.  Those areas most directly connected to the trading partner will be more likely to experience violent conflict than those areas that are less dependent on the trading partner.  They operationalize this measure of dependence, or ``remoteness,'' as distance from a seaport.  Indeed, they find that conflicts are more likley to arise near seaports following an economic shock than they are further away.

>>>>

That civil wars negatively impact economic performance, while in line with the ``war ruin'' hypothesis, runs counter to the ``war renewal'' hypothesis.  Some scholars have argued that wars, international wars in particular, can spur economic development\footnote{For a review of this discussion, see \cite{rasler:thompson:1985}}.  The prevailing wisdom with regard to civil war, however, is that outcomes of this nature are the exception rather than the rule.  In a test of economic and social determinants of post-conflict recovery in the context of civil war, \cite{kang:meernik:2005} find that these conflicts can lead, under different conditions, to either rapid or stagnant economic recovery.  They conclude that the long-term economic impacts of civil war are largely dependent on post-war governance and foreign assistance.  They also find, perhaps unsuprisingly, that aggregate estimates of conflict destructiveness are negatively correlated with long-term growth.

Not only do several studies link civil war to domestic economic performance, there is also evidence that civil wars have regional economic consequences.  \cite{murdoch:sandler:2002a} find some evidence that states neighboring civil war states are more likely to experience poor short-term economic performance.  They attribute this effect to the disruption of trade and uncertainty about the potential for conflict to spread across the border.  In a follow up study, \cite{murdoch:sandler:2002b} suggest that the spatial dispersion of economic effects from civil conflict differ from region to region.

@@

\cite{berman:couttenier:2013} explore another sub-state determinant of civil conflict.  Recognizing that economic shocks are associated with changes to the probability of civil conflict,\footnote{For more, see \cite{miguel:etal:2004} and \cite{dube:vargas:2013}.} they seek to determine where conflict will emerge when these shocks occur.  Given an external economic shock in a trading partner, Berman and Couttenier expect that states should be at an increased risk of experiencing conflict.  However, not all locations within a state will feel the effects equally.  Those areas most directly connected to the trading partner will be more likely to experience violent conflict than those areas that are less dependent on the trading partner.  They operationalize this measure of dependence, or ``remoteness,'' as distance from a seaport.  Indeed, they find that conflicts are more likley to arise near seaports following an economic shock than they are further away.

\cite{buhaug:2010} argues that the geography of conflict is a function of rebel strength.  In particular, strong rebel groups are able to conduct military operations near capital cities while weak ones are not.  These weaker groups are only able to survive in areas more distant from capitals.
